Notes on the low density parameters in {\tt MAESTRO}

### 2009-02-10 docs/lo_density/lo_density.tex
fixed a minor error
for spherical, correct base everywhere, not just inside the anelastic cutoff

\item In {\tt correct\_base}, we only update $\rho_0$ for 
  $r\in[{\tt r\_start\_coord},{\tt anelastic\_cutoff\_coord}-1]$.

@@

\item In {\tt make\_psi}, we only compute $\psi$ for 
  $r\in[{\tt r\_start\_coord},{\tt anelastic\_cutoff\_coord}-1]$.

>>>>

@@

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r\in[{\tt r\_start\_coord},{\tt anelastic\_cutoff\_coord}-1]$.
